Replication Survey

### 2024-02-06 docs/manuscript/manuscript.tex
Updates from Overleaf

\author{
\name{Peter Kedron\textsuperscript{a,b}\thanks{CONTACT Peter Kedron. Email: peterkedron@ucsb.edu}, Joseph Holler\textsuperscript{d}, and Sarah Bardin\textsuperscript{a,c}}
\affil{\textsuperscript{a} Department of Geography, University of California Santa Barbara, Santa Barbara, California, USA; \textsuperscript{b}School of Geographical Sciences and Urban Planning, Arizona State University, Tempe, Arizona, USA; \textsuperscript{c}Spatial Analysis Research Center (SPARC), Arizona State University, Tempe, Arizona, USA; \textsuperscript{d}Department of Geography, Middlebury College, Middlebury, Vermont, USA}
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\section*{Introduction}
Replications confront existing explanations with new evidence by retesting prior claims using new data and similar research procedures.
Replications can be designed to serve different epistemic functions and to test several forms of validity.
Attempts to reproduce prior research may also test the validity of a study, but do so using the same data and the same, or very similar, analyses. 
Contrasted with a replication attempt, the central focus of a reproduction attempt is the verification of claims through the examination of how a study was conducted and whether the design and execution of that study support the results presented.
While the results of a reproduction or replication do not provide conclusive evidence for or against a claim, those that produce outcomes consistent with prior studies typically increase confidence in a claim and the theories it is based on \citep{earp2015, nichols2021}. 
When prior results cannot be recreated, there is reason to question the data and methods used by the prior study, the claims made by the prior study, and perhaps even the current theoretical understanding of the geographic phenomena \citep{christensen2019, NASEM2019}.

@@

The small number of published studies that have attempted to replicate geographic research suggest that many studies cannot be fully replicated \citep[e.g.,][]{Kedron2022dimaggio, paez2022reproducibility}, or are simply missing components needed to attempt a replication \citep{konkol2019, ostermann2017}.
More often the literature on the replication of geographic research turns to the question of if and when it is reasonable to expect the findings and claims of a prior study to replicate \citep{kedron2021GA, kedron2022replication, goodchild2021replication, sui2021reproducibility}. 
Place-to-place variations in phenomena, and the processes that produce those variations, are one of the defining features of geographic research and a central tenet of many of its research traditions.
With these intellectual foundations, it remains unclear how current geographic researchers view replication and its role of in the knowledge accumulation process.
There is similarly limited empirical evidence available about the factors that motivate or discourage geographic researchers from pursuing replications.

To address this gap in our collective knowledge, we surveyed geographic researchers about their understanding of replicability, beliefs about what factors affects the chances or replicating a study, motivations to attempt replication studies, and experiences conducting replications.
We are aware of only a handful of similar published surveys within the geographic literature \citep{balz2020reproducibility, konkol2019, ostermann2017, kedron2023survey}.
However, these surveys typically focus on the quantitative and computational intensive forms of geographic research, primarily assess the availability of research artifacts (e.g., data and code), and address reproducibility rather than replicability. 
In all but one instance, these surveys also rely on convenience samples drawn from specialist conferences or non-representative subsets of the geographic research community. 
In contrast, to support generalization, we designed a sampling frame to capture researchers from across disciplinary subfields and methodological approaches, and draw survey participants from that frame using a probability sampling scheme.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Replication and the Evaluation of Prior Claims}
Replications structure the iterative development of theory by confronting claims with new evidence.
Broadly defined, a replication is any study that has at least one outcome that would be considered diagnostic evidence of the validity of a claim made in prior research \citep{nosek2020}.
No single study provides evidence about all of the conditions that could affect a claim because individual studies are performed by particular researchers using particular methods to draw and analyze data from particular settings. 
Until a claim is tested through replication, our expectation of whether it will hold under new conditions relies on the theory used to structure the original investigation, or on a speculative assumption of generalizability.
Replications empirically test the validity and reliability of the claims made in a study by selectively altering different aspects of the initial work and repeating the study \citep{schmidt2009, gomez2010replications, radder2003, radder2012}.  
By altering different aspects of a study across a series of replications, researchers can collectively and progressively test claims across a widening set of conditions and use that information to revise theory.

The type of check a replication provides depends on which aspects of a study are changed and in what combination. 
Researchers pursuing a replication will collect new data, but will also change the materials and procedures used in the replication, the measurement of variables, the location of the replication, and/or the population being studied \citep{hendrick1990, schmidt2009, gomez2010replications}. 
Replication studies are often classified as either direct or conceptual based on which of these aspects a research is changing and the epistemological objective they are pursuing \citep[see][]{sargent1981repeatability, schmidt2009, plesser2018reproducibility}.

Direct replications make limited changes to an initial study in order to verify the claims of the study by testing for conclusion, construct, and internal validity. 
If a researcher attempting a replication keeps all aspects of a study the same, but collects new data, then the replication is designed to assess conclusion validity.
As long as the population being studied remains stable between the two studies, the replication will control for sampling error and will provide evidence as to whether the prior results were the product of chance variation. 
Alternatively, if a researcher changes how a key construct is measured and also holds all other aspects of a study constant, then the replication can test construct validity.
Consistently observing a relationship across well-established measures of a concept or phenomenon may raise researcher confidence that the operationalization used in the original study did not bias the result, or affect the claims made. 
Finally, if the materials and procedures (e.g., data collection device, analyses) used in a replication differ from a prior study, then the replication assesses whether these factors affected the original results, thereby testing the internal validity of the prior work.

In conceptual replications, changes are made to the population or location being studied in order to test external validity and whether the claims made in a study generalize to new populations and contexts. 
In geographic research, a conceptual replication could involve changing the location of a study from one city to another, or from one ecosystem to another. 
Alternatively, a researcher could could conduct a conceptual replication of a study by examining the same location after migration is thought to have changed the population of that area. 
Conceptual replications provide evidence that can be used to assess the hypotheses and theories that underlie a prior study in new situations \citep{schmidt2009}.
However, conceptual replications do not necessarily provide evidence that can be used to adjust confidence in a claim made in an initial study \citep{nosek2020}.
For example, it is not necessarily the case that observing evidence in one location that contradicts a claim made in a prior study of another location would cause a researcher to reduce their confidence in the prior claim.

As tests of generalizability and external validity, conceptual replications play an important role in the development of theory \citep{earp2015, haig2022, irvine2021}.
When a theory is early in its development, it is often unclear whether a researcher should expect the predictions of that theory to hold in new populations, spaces, and times.
This is the case because new theories commonly lack a well developed set of conditional statements identifying for whom, where, and/or when their explanations and predictions should hold. 
Without these statements, it remains possible that the predictions of the theory will generalize across a large set of contexts. 
In other words, a lack of evidence causes uncertainty about the explanatory range of the theory.
In this situation, conceptual replications act as empirical tests of the generalizability of a theory to new contexts. 
Conceptual replications provide evidence to inform the addition and revision of conditional statements that identify for whom, where, and /or when the theory is expected to provide meaningful predictions.
As the conditions required for a claim to replicate are incorporated into the theory, the theory matures and the situations in which the prediction of the theory are expected to hold becomes clear.

@@

The first point raised in most discussions of replication in geography is that places are unavoidably different from one another \citep[see][]{goodchild2021Annals, goodchild2022reproducibility, Wainwright2021}.
Researchers involved in these discussions often invoke \cite{anselin1989special} second law of geography which notes that geographic features exhibit uncontrolled variability over space. 
This principle implies that researchers can expect to observe differences between places, and that perhaps they should expect an inability to replicate prior findings from one place in another.
Geographic variation essentially poses an identification problem for those interpreting the results of a replication because it is not clear whether the same research outcome (e.g., parameter estimates) observed in different locations is or is not determined by the same processes.  
In some instances, commentary about differences between places are combined  with discussions of role of researcher position and perspective in the research process \citep{Peet1999, simandan2019revisiting}. 
Discussions of replication developed from this perspective often suggest that the role replication can play in geography is limited because research is an interpretive process dependent on the unique perspective of a researcher who is analyzing data drawn from different or unique places \citep{Wainwright2021}.

Arguments about geographic variation can be pushed further and linked the principle of flux \citep{marcovich1967}, which, alternatively argues on one hand that phenomena studied in a place cannot be encountered twice, or on the other hand that places are defined not by the stability of their features but by their continual renewal through processes that create change in those same features. 
The two alternative readings of this principle have very different implications for the prospect of replicating geographic research.
Under the first simpler reading, change is constant and a researcher should not expect to find the same arrangement of features at different times in the same location.
In this situation, an inability replicate a finding would not be surprising and explanations would be localized. 
Under the second reading, geographic features are continually changing but structured by processes that may, or may not, be consistent across time and space. 
In this situation, findings may be expected to replicate within a range of uncertainty, and attempting replications can give insight into the stability of processes across locations.

Understanding places as defined by processes that potentially differ across locations aligns with the argument that geography is well-suited to the development of empirically grounded middle-range theory \citep{miller2015data}.
The aim of middle-range theory is not to develop overarching explanations or essential features of processes, but rather to offer provisional explanations of identifiable phenomena which can be tested and used to slowly develop more general but bounded explanations \citep{merton1968social}.
As \cite{harvey1969} notes, geographers often elaborate the theories of other disciplines by linking them with spatial explanations of form and process.
\cite{turner1989, turner2002} argues this synthesis approach gives geography the capability to generate and refine the text of theories and establish their spatial domain by examining phenomena empirically within a web of complex processes that interact within and between locations. 
In this way, replications can give insight into when, where, and why a explanation does not hold \citep{zhang_wolf_2023}.
Similarly, \cite{sayer1992method} distinguishes between intensive research in which synthesis is used to identify how processes work in a particular case of location, and extensive research in which synthesis extends across cases or locations to identify how widely a process holds. 
In intensive research, replication attempts that change the data collected from a location can be used to corroborate the explanation of a process.
In extensive research, replication data is gathered from new context to establish the coverage of an explanation. 
In either case, that accumulation of empirical evidence through replication can be used to refine and adjust theory.

Finally, discussions of replication in the literature also frequently point out that many of the phenomena geographers study not only vary across locations, but are difficult or impossible to control \citep[see][]{sayer1992method, kedron2021GA, waters2021motivations}. 
In practice, geographers often lack the ability to control where data is collected, which populations are included or excluded in a study, how variables are measured, and the materials and procedures used when attempting a replication.
This lack of control makes it difficult to execute replications that isolate the influence of any particular factor, which makes it unclear what lessons should be learned from a replication attempt and what epistemological function that attempt may be serving. 
Moreover, it is also often unclear which factors should be accounted for when studying a particular location.
As \cite{goodchild2021replication} suggest, even when some level of control can be exerted on a process, it will remain difficult to exclude the variable effects of context from studies that are incompletely identified in the presence of spatially heterogeneity.
While these factors make replication practically challenging in some forms of geographic research, they do not themselves eliminate the potential usefulness of the practice in selected cases.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Data and Methods}
Complete documentation of the procedures, survey instrument, and other materials used in this study are available through the Survey of Researcher Perceptions of Replication in Geography project (\citet{Kedron_Holler_Bardin_Hilgendorf_2022} - \url{https://osf.io/x6qrk/}).
That OSF project connects to a GitHub repository which hosts the anonymized dataset and code used to create all results and supplemental materials along with a complete history of their development. 
All of the results presented in this paper can be independently reproduced using the materials in that repository.
Before the start of data collection, we preregistered an analysis plan for the survey with OSF Registries (\citet{Kedron_RPl_Survey_PAP} - \url{https://osf.io/a4nwg}). 
The survey was conducted under the approval and supervision of the Arizona State Institutional Review Board - \textit{STUDY00014232}.

@@

Fourth, we constructed a sampling frame of unique researchers and their most recent email contact information. 
We determined uniqueness by grouping researchers by their author-id, and we determined the most recent contact information by selecting records associated with the most recent year of publication. 
For 383 researchers who had two or more distinct emails in the latest year of publication, we removed non-institutional personal email addresses and then selected one of the remaining institutional email address.

@@

\noindent Remaining questions assessed the epistomological purpose of a replication (5 questions), what portion of the geographic literature has/could/should be replicated (3 questions), and factors that impact the chances of successfully replicating a study (18 questions) or the decision to attempt a replication (13 questions).
For researchers who reported attempting reproductions, we asked them to elaborate on their motivations and outcomes (9 questions).

We developed the survey questions following a review of prior reproducibility surveys \citep[e.g.,][]{fanelli2009many,baker20161, konkol2019} and our own reading of recurring issues in the reproducibility and replicability literature. 
We pilot tested the survey instrument with \textit{n}=15 graduate students and geography faculty with differing levels of experience, topical focus, and methodological background. 
After pilot testing, we removed these individuals from our sampling frame to ensure they would not be included in our final sample.

@@

The online survey was administered through \href{https://www.qualtrics.com/}{Qualtrics}. 
Participation in the survey was entirely voluntary. 
Each researcher that opted to participate in the survey was provided with IRB approved consent documentation and linked to the internet survey instrument. 
Participants were also given the option to provide an email address for eligibility for one of three  prizes of 90 US\$, selected randomly after the data collection period.
Participating researchers had the option to exit and re-enter the survey and were also able to review and change their answers using a back button as they progressed through the survey.
At the end of the data collection period, responses were checked for completeness and coded using the reporting standards of the American Association For Public Opinion Research \citep{aaporstandards}.
Responses were downloaded from Qualtrics, anonymized, and stored in a public de-identified database in the research compendium.

@@

We conducted two analyses of the survey responses.
First, we analyzed researcher perspectives on replicability by coding and calculating summary variables and statistics for three themes: how geographic researchers define replicability, factors researchers believe affect the decision to attempt to replicate a study, and factors researchers believe affect the chances of sucessfully replicating a study.
Second, we analyzed the experiences of researchers attempting to replicate prior studies using statistical summaries of participant motivations, research practices, and ability to produce results consistent with prior studies.
For both analyses, we produced and analyzed descriptive statistical summaries of participant responses to Likert scale questions cross-tabulated by disciplinary subfield and methodological approach.
For free-from text responses we coded responses and selected illustrative examples for inclusion.

For free-form text definitions of ``replicability'' we coded participant responses using two procedures. 
First, we measured the similarity of each provided definition to the definition adopted by the \citet{NASEM2019}. 
The NASEM defines reproducible research as having three characteristics --- new data, same procedure, and same or similar results.
To make this comparison, two of the authors independently coded each respondent definition for the presence/absence of each of these the three characteristics.
Disagreements in the assignment of codes were resolved through discussion between the three authors.
We created an aggregate measure of definition similarity for the final coded response for each participant by counting the presence of each NASEM definition characteristic, resulting in a measure with the domain [0, 3].

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Results}
A total of \textit{n}=283 of the authors we contacted completed the online survey with information sufficient for analysis. 
The contact rate for the survey was 18.8 percent, the response rate was 14.1 percent, yielding a cooperation rate of 74.4 percent. 
The refusal rate was 4.8 percent\endnote{All outcome rates are reported using \citet{aaporstandards} standards. 
The outcome rates used were - response rate 2, cooperation rate 2, refusal rate 1, and contact rate 1.}.
Respondents were predominantly male (65.1\%) and between the ages of 35 and 55 (62.4\%). 
The majority of respondents were also academics, but were well balanced across career levels as no one category made up more that 30 percent of the sample.
Respondents were similarly balanced across disciplinary subfields, but did contain a greater number of physical geographers  - human geography (26.8\%), physical geography (39.9\%), nature and society (14.8\%), geographic methods and GIScience (17.3\%). 
Different methodological approaches were well represented by respondents in the sample with qualitative researchers making up the smallest sub-group  - quantitative (47.3\%), qualitative (16.3\%), and mixed-methods (36.0\%).

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Researcher Definitions of Replication and its Epistemic Functions}
Geographic researchers are thinking about replicability and link the act of replicating a study to a number of different epistemological functions. 
A majority of respondents reported thinking about replicability (74\%), talking with colleagues about replicability (65\%), and considering replicability when undertaking peer-review (59\%) during the past two years. 
Specifically, respondents believe that replication studies can assess whether the claims of that study will hold in new locations (67\%) or new populations (63\%) (Figure \ref{fig:Q7-Epistemology}).
Respondents also believe that replication studies can be used to investigate and assess whether the variables used in prior studies reflect the concepts that intended to represent (76\%) and whether prior findings resulted from chance variation (66\%).
While respondents clearly linked replication to epistemological functions, across all functions they were more likely to agree than to strongly agree that replications could serve these purposes.
Respondents that identified as human geographers or as studying nature and society were less likely to agree that replications could be used to achieve these goals when compared to those working in other subfields. 
For example, 87 percent of respondents specializing in GIScience and methods believe replications could be used to assess whether a claim was the product of chance, compared to just 57 percent of human and nature-society researchers.

@@

Respondents were generally uncertain or pessimistic about how the characteristics of the researchers and teams of prior studies would change the chances of replicating the studies. 
A majority of respondents (51\%) indicated that a large research team working on the prior study would have no effect on the chances of an independent researcher replicating that work. 
The remaining respondents were nearly evenly split as to whether a large team would increase of decrease the chances of replicating that study. 
More respondents believed that reliance on the unique expertise (48\%) or unique position(s) (53\%) of the researcher(s)  conducting a study would decrease, rather than increase, the chances of replicating the claims of a study.
In both cases, 24 percent of respondents reported that they did not believe either factor would impact the odds of replicating a prior result.

>>>>

\author{
\name{Peter Kedron\textsuperscript{a,b}\thanks{CONTACT Peter Kedron. Email: peterkedron@ucsb.edu}, Joseph Holler\textsuperscript{c}, and Sarah Bardin\textsuperscript{b,d}}
\affil{\textsuperscript{a} Department of Geography, University of California Santa Barbara, Santa Barbara, California, USA; \textsuperscript{b}School of Geographical Sciences and Urban Planning, Arizona State University, Tempe, Arizona, USA; \textsuperscript{c}Department of Geography, Middlebury College, Middlebury, Vermont, USA
\textsuperscript{d}Spatial Analysis Research Center (SPARC), Arizona State University, Tempe, Arizona, USA; }
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\section*{Introduction}
Replications confront existing explanations with new evidence by retesting prior claims using new data and similar research procedures.
Replications can be designed to serve different epistemic functions and to test several forms of validity.
Attempts to reproduce prior research may also test the validity of a study, but do so using the same data and the same, or very similar, analyses. 
Contrasted with a replication attempt, the central focus of a reproduction attempt is the verification of claims through the examination of how a study was conducted and whether the design and execution of that study supports the results presented.
While the results of a reproduction or replication do not provide conclusive evidence for or against a claim, those that produce outcomes consistent with prior studies typically increase confidence in a claim and the theories upon which it is based \citep{earp2015, nichols2021}. 
When prior results cannot be recreated, there is reason to question the data and methods used by the prior study, the claims made by the prior study, and perhaps even the current theoretical understanding of the geographic phenomena \citep{christensen2019, NASEM2019}.

@@

The small number of published studies that have attempted to replicate geographic research suggest that many studies cannot be fully replicated \citep[e.g.,][]{Kedron2022dimaggio, paez2022reproducibility}, or are simply missing components needed to attempt a replication \citep{konkol2019, ostermann2017}.
More often the literature on the replication of geographic research turns to the question of if and when it is reasonable to expect the findings and claims of a prior study to be replicable \citep{kedron2021GA, kedron2022replication, goodchild2021replication, sui2021reproducibility}. 
Place-to-place variations in phenomena, and the processes that produce those variations, are one of the defining features of geographic research and a central tenet of many of its research traditions.
With these intellectual foundations, it remains unclear how current geographic researchers view replication and its role in the knowledge accumulation process.
There is similarly limited empirical evidence available about the factors that motivate or discourage geographic researchers from pursuing replications.

To address this gap in our collective knowledge, we surveyed geographic researchers about their understanding of replicability, beliefs about what factors affect the chances of replicating a study, motivations to attempt replication studies, and experiences conducting replications.
We are aware of only a handful of similar published surveys within the geographic literature \citep{balz2020reproducibility, konkol2019, ostermann2017, kedron2023survey}.
However, these surveys typically focus on the quantitative and computational intensive forms of geographic research, primarily assess the availability of research artifacts (e.g., data and code), and address reproducibility rather than replicability. 
In all but one instance, these surveys also rely on convenience samples drawn from specialist conferences or non-representative subsets of the geographic research community. 
In contrast, to support generalization, we designed a sampling frame to capture researchers from across disciplinary subfields and methodological approaches, and draw survey participants from that frame using a probability sampling scheme.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Replication and the Evaluation of Prior Claims}
Replications structure the iterative development of theory by confronting claims with new evidence.
Broadly defined, a replication is any study that has at least one outcome that would be considered diagnostic evidence of the validity of a claim made in prior research \citep{nosek2020}.
No single study provides evidence about all conditions that could affect a claim, because individual studies are performed by particular researchers using particular methods to draw and analyze data from particular settings. 
Until a claim is tested through replication, our expectation of whether it will hold under new conditions relies on the theory used to structure the original investigation or on a speculative assumption of generalizability.
Replications empirically test the validity and reliability of the claims made in a study by selectively altering different aspects of the initial work and repeating the study \citep{schmidt2009, gomez2010replications, radder2003, radder2012}.  
By altering different aspects of a study across a series of replications, researchers can collectively and progressively test claims across a widening set of conditions and use that information to revise theory.

The type of check a replication provides depends on which aspects of a study are changed and in what combination. 
Researchers pursuing a replication will collect new data, but will also change the materials and procedures used in the replication, the measurement of variables, the location of the replication, and/or the population being studied \citep{hendrick1990, schmidt2009, gomez2010replications}. 
Replication studies are often classified as either direct or conceptual depending on which of these aspects a researcher is changing and the epistemological objective they are pursuing \citep[see][]{sargent1981repeatability, schmidt2009, plesser2018reproducibility}.

Direct replications make limited changes to an initial study in order to verify the claims of the study by testing for conclusion, construct, and internal validity. 
If a researcher attempting a replication keeps all aspects of a study the same, but collects new data, then the replication is designed to assess conclusion validity.
As long as the population being studied remains stable between the two studies, the replication will control for sampling error and will provide evidence as to whether the prior results were the product of chance variation. 
Alternatively, if a researcher changes how a key construct is measured and also holds all other aspects of a study constant, then the replication can test construct validity.
Consistently observing a relationship across well-established measures of a concept or phenomenon may raise researcher confidence that the operationalization used in the original study did not bias the result or affect the claims made. 
Finally, if the materials and procedures (e.g., data collection device, analyses) used in a replication differ from a prior study, then the replication assesses whether these factors affected the original results, thereby testing the internal validity of the prior work.

In conceptual replications, changes are made to the population or location being studied in order to test external validity and whether the claims made in a study generalize to new populations and contexts. 
In geographic research, a conceptual replication could involve changing the location of a study from one city to another or from one ecosystem to another. 
Alternatively, a researcher could conduct a conceptual replication of a study by examining the same location across different time periods, for instance, before and after migration is thought to have changed the population within that area. 
Conceptual replications provide evidence that can be used to assess the hypotheses and theories that underlie a prior study in new situations \citep{schmidt2009}.
However, conceptual replications do not necessarily provide evidence that can be used to adjust confidence in a claim made in an initial study \citep{nosek2020}.
For example, it is not necessarily the case that observing evidence in one location that contradicts a prior study's claim based on a different location should reduce a researcher's confidence in the prior claim.

As tests of generalizability and external validity, conceptual replications play an important role in the development of theory \citep{earp2015, haig2022, irvine2021}.
When a theory is early in its development, it is often unclear whether a researcher should expect the predictions of that theory to hold in new populations, locations, and times.
This is the case because new theories commonly lack a well developed set of conditional statements identifying for whom, where, and/or when their explanations and predictions should hold. 
Without these statements, it remains possible that the predictions of the theory will generalize across a large set of contexts. 
In other words, a lack of evidence causes uncertainty about the explanatory range of the theory.
In this situation, conceptual replications act as empirical tests of the external validity of a theory. 
Conceptual replications provide evidence to inform the addition and revision of conditional statements that identify for whom, where, and/or when the theory is expected to provide meaningful predictions.
As the conditions required for a claim to replicate are incorporated into the theory, the theory matures and the situations in which the prediction of the theory are expected to hold becomes clearer.

@@

The first point raised in most discussions of replication in geography is that places are unavoidably different from one another \citep[see][]{goodchild2021Annals, goodchild2022reproducibility, Wainwright2021}.
Researchers involved in these discussions often invoke \cite{anselin1989special} second law of geography which notes that geographic features exhibit uncontrolled variability over space. 
This principle implies that researchers can expect to observe differences between places, which may contribute to an inability to replicate prior findings from one place in another.
Geographic variation essentially poses an identification problem for those interpreting the results of a replication, because it is not clear whether the same research outcome (e.g., parameter estimates) observed in different locations is or is not determined by the same processes.  
In some instances, commentary about differences between places are combined  with discussions of role of researcher position and perspective in the research process \citep{Peet1999, simandan2019revisiting}. 
Discussions of replication developed from this perspective often suggest that the role replication can play in geography is limited, because research is an interpretive process dependent on the unique perspective of a researcher who is analyzing data drawn from different or unique places \citep{Wainwright2021}.

Arguments about geographic variation can be pushed further and linked to the principle of flux \citep{marcovich1967}. 
This alternative argument suggests that, on the one hand, phenomena studied in a place cannot be encountered twice, and, on the other hand, that places are defined not by the stability of their features but by their continual renewal through processes that create change in those same features. 
The two alternative readings of this principle have very different implications for the prospect of replicating geographic research.
Under the first simpler reading, change is constant and a researcher should not expect to find the same arrangement of features at different times in the same location.
In this situation, an inability to replicate a finding would not be surprising and explanations would be localized. 
Under the second reading, geographic features are continually changing but are structured by processes that may, or may not, be consistent across time and space. 
In this situation, findings may be expected to replicate within a range of uncertainty, and attempting replications can give insights into the stability of processes across locations.

Understanding places as defined by processes that potentially differ across locations aligns with the argument that geography is well-suited to the development of empirically grounded middle-range theory \citep{miller2015data}.
The aim of middle-range theory is not to develop overarching explanations or essential features of processes, but rather to offer provisional explanations of identifiable phenomena, which can be tested and used to slowly develop more general but bounded explanations \citep{merton1968social}.
As \cite{harvey1969} notes, geographers often elaborate the theories of other disciplines by linking them with spatial explanations of form and process.
\cite{turner1989, turner2002} argues this synthesis approach gives geography the capability to generate and refine the text of theories and establish their spatial domain by examining phenomena empirically within a web of complex processes that interact within and between locations. 
In this way, replications can give insight into when, where, and why an explanation does not hold \citep{zhang_wolf_2023}.
Similarly, \cite{sayer1992method} distinguishes between intensive research in which synthesis is used to identify how processes work in a particular case of location, and extensive research in which synthesis extends across cases or locations to identify how widely a process holds. 
In intensive research, replication attempts that change the data collected from a location can be used to corroborate the explanation of a process.
In extensive research, replication data is gathered from new contexts to establish the coverage of an explanation. 
In either case, that accumulation of empirical evidence through replication can be used to refine and adjust theory.

Finally, discussions of replication in the literature also frequently point out that many of the phenomena geographers study not only vary across locations but are difficult or impossible to control \citep[see][]{sayer1992method, kedron2021GA, waters2021motivations}. 
In practice, geographers often lack the ability to control where data is collected, which populations are included or excluded in a study, how variables are measured, and the materials and procedures used when attempting a replication.
This lack of control makes it difficult to execute replications that isolate the influence of any particular factor, which makes it unclear what lessons should be learned from a replication attempt and what epistemological function that attempt may be serving. 
Moreover, it is also often unclear which factors should be accounted for when studying a particular location.
As \cite{goodchild2021replication} suggest, even when some level of control can be exerted on a process, it will remain difficult to exclude the variable effects of context from studies that are incompletely identified in the presence of spatial heterogeneity.
While these factors make replication practically challenging in some forms of geographic research, they do not themselves eliminate the potential usefulness of the practice in selected cases.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Data and Methods}
Complete documentation of the procedures, survey instrument, and other materials used in this study are available through the Survey of Researcher Perceptions of Replication in Geography project (\citet{Kedron_Holler_Bardin_Hilgendorf_2022} - \url{https://osf.io/x6qrk/}).
This OSF project connects to a GitHub repository which hosts the anonymized dataset and code used to create all results and supplemental materials along with a complete history of their development. 
All of the results presented in this paper can be independently reproduced using the materials in that repository.
Before the start of data collection, we preregistered an analysis plan for the survey with OSF Registries (\citet{Kedron_RPl_Survey_PAP} - \url{https://osf.io/a4nwg}). 
The survey was conducted under the approval and supervision of the Arizona State Institutional Review Board - \textit{STUDY00014232}.

@@

Fourth, we constructed a sampling frame of unique researchers and their most recent email contact information. 
We determined uniqueness by grouping researchers by their author-id, and we determined the most recent contact information by selecting records associated with the most recent year of publication. 
For 383 researchers who had two or more distinct emails in the latest year of publication, we removed non-institutional personal email addresses and then selected one of the remaining institutional email addresses.

@@

\noindent Remaining questions assessed the epistemological purpose of a replication (5 questions), what portion of the geographic literature has/could/should be replicated (3 questions), and factors that impact the chances of successfully replicating a study (18 questions) or the decision to attempt a replication (13 questions).
For researchers who reported attempting reproductions, we asked them to elaborate on their motivations and outcomes (9 questions).

We developed the survey questions following a review of prior reproducibility surveys \citep[e.g.,][]{fanelli2009many,baker20161, konkol2019} and our own reading of recurring issues in the reproducibility and replicability literature. 
We pre-tested the survey instrument with \textit{n}=15 graduate students and geography faculty with differing levels of experience, topical focus, and methodological background. 
After pilot testing, we removed these individuals from our sampling frame to ensure they would not be included in our final sample.

@@

The online survey was administered through \href{https://www.qualtrics.com/}{Qualtrics}. 
Participation in the survey was entirely voluntary. 
Each researcher that opted to participate in the survey was provided with IRB-approved consent documentation and linked to the internet survey instrument. 
Participants were also given the option to provide an email address for eligibility for one of three  prizes of 90 US\$, selected randomly after the data collection period.
Participating researchers had the option to exit and re-enter the survey and were also able to review and change their answers using a back button as they progressed through the survey.
At the end of the data collection period, responses were checked for completeness and coded using the reporting standards of the American Association For Public Opinion Research \citep{aaporstandards}.
Responses were downloaded from Qualtrics, anonymized, and stored in a public de-identified database in the research compendium.

@@

We conducted two analyses of the survey responses.
First, we analyzed researcher perspectives on replicability by coding and calculating summary variables and statistics for three themes: how geographic researchers define replicability, factors researchers believe affect the decision to attempt to replicate a study, and factors researchers believe affect the chances of successfully replicating a study.
Second, we analyzed the experiences of researchers attempting to replicate prior studies using statistical summaries of participant motivations, research practices, and ability to produce results consistent with prior studies.
For both analyses, we produced and analyzed descriptive statistical summaries of participant responses to Likert scale questions cross-tabulated by disciplinary subfield and methodological approach.
For free-form text responses we coded responses and selected illustrative examples for inclusion.

For free-form text definitions of ``replicability'' we coded participant responses using two procedures. 
First, we measured the similarity of each provided definition to the definition adopted by the \citet{NASEM2019}. 
The NASEM defines replicable research as having three characteristics --- new data, same procedure, and same or similar results.
To make this comparison, two of the authors independently coded each respondent definition for the presence/absence of each of these three characteristics.
Disagreements in the assignment of codes were resolved through discussion between the three authors.
We created an aggregate measure of definition similarity for the final coded response for each participant by counting the presence of each NASEM definition characteristic, resulting in a measure with the domain [0, 3].

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Results}
A total of \textit{n}=283 of the authors we contacted completed the online survey with information sufficient for analysis. 
The contact rate for the survey was 18.8 percent, the response rate was 14.1 percent, yielding a cooperation rate of 74.4 percent. 
The refusal rate was 4.8 percent\endnote{All outcome rates are reported using \citet{aaporstandards} standards. 
The outcome rates used were - response rate 2, cooperation rate 2, refusal rate 1, and contact rate 1.}.
Respondents were predominantly male (65.1\%) and between the ages of 35 and 55 (62.4\%). 
The majority of respondents were also academics, but were well-balanced across career levels as no one category made up more that 30 percent of the sample.
Respondents were similarly balanced across disciplinary subfields but did contain a greater number of physical geographers  - human geography (26.8\%), physical geography (39.9\%), nature and society (14.8\%), geographic methods and GIScience (17.3\%). 
Different methodological approaches were well-represented by respondents in the sample with qualitative researchers making up the smallest sub-group  - quantitative (47.3\%), qualitative (16.3\%), and mixed-methods (36.0\%).

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Researcher Definitions of Replication and its Epistemic Functions}
Geographic researchers are thinking about replicability and link the act of replicating a study to a number of different epistemological functions. 
A majority of respondents reported thinking about replicability (74\%), talking with colleagues about replicability (65\%), and considering replicability when undertaking peer-review (59\%) during the past two years. 
Specifically, respondents believe that replication studies can assess whether the claims of that study will hold in new locations (67\%) or new populations (63\%) (Figure \ref{fig:Q7-Epistemology}).
Respondents also believe that replication studies can be used to investigate and assess whether the variables used in prior studies reflect the concepts that they were intended to represent (76\%) and whether prior findings resulted from chance variation (66\%).
While respondents clearly linked replication to epistemological functions, across all functions they were more likely to agree than to strongly agree that replications could serve these purposes.
Respondents that identified as human geographers or as studying nature and society were less likely to agree that replications could be used to achieve these goals when compared to those working in other subfields. 
For example, 87 percent of respondents specializing in GIScience and methods believe replications could be used to assess whether a claim was the product of chance, compared to just 57 percent of human and nature-society researchers.

@@

Respondents were generally uncertain or pessimistic about how the characteristics of the researchers and teams of prior studies would change the chances of replicating the studies. 
A majority of respondents (51\%) indicated that a large research team working on the prior study would have no effect on the chances of an independent researcher replicating that work. 
The remaining respondents were nearly evenly split as to whether a large team would increase or decrease the chances of replicating that study. 
More respondents believed that reliance on the unique expertise (48\%) or unique position(s) (53\%) of the researcher(s)  conducting a study would decrease, rather than increase, the chances of replicating the claims of a study.
In both cases, 24 percent of respondents reported that they did not believe either factor would impact the odds of replicating a prior result.
